Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-20 paper/ms.tex
update ms

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
\ngoods\ CQVs.  The objects are sorted first in order of the
number of TESS 120-second cadence sectors in which they clearly
demonstrated the CQV phenomenon, and secondarily by descending
brightness.  The top five objects by this metric are TIC~300651846
($T$$=$13.5, 12 sectors); TIC~402980664 ($T$$=$11.1, 7 sectors);
TIC~89463560 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5
sectors); and TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest
five CQVs span 9.3$<$$T$$<$11.1; the faintest five span
14.5$<$$T$$<$15.0.  The fastest five have periods spanning
3.6\,hr$<$$P$$<$6.2\,hr, and the slowest five span
27\,hr$<$$P$$<$38\,hr.

@@

The most massive CQV in our sample is a subject of some interest.  To
date, the only stars reported to show the CQV phenomenon are M-dwarfs,
with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2022AJ....163..144G}.  TIC~405754448 and 405910546 however
appear to have masses of 0.82 and 0.60\,$M_\odot$ respectively.  The
next-highest masses are $\approx$0.40\,$M_\odot$.  The masses for the
former two objects are consistent with their CAMD locations, and their
membership in LCC.  Based on its light curve morphology, TIC~405910546
should be studied in greater depth, to confirm it is not an eclipsing
binary.  TIC~405754448 similarly shows distinct morphology from many
of the CQVs in Figure~\ref{fig:cqvs}, in that it has some of the
lowest amplitude dips.  Nonetheless, both of these objects seem to
suggest that the CQV phenomenon extends up in mass to
pre-main-sequence K-dwarfs.

>>>>

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
\ngoods\ CQVs.  The objects are sorted first in order of the
number of TESS 120-second cadence sectors in which they clearly
demonstrated the CQV phenomenon, and secondarily by descending
brightness.  The top five objects by this metric are TIC~300651846
($T$$=$13.5, 12 sectors); TIC~402980664 ($T$$=$11.1, 7 sectors);
TIC~89463560 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5
sectors); and TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest
five CQVs span 9.3$<$$T$$<$11.1; the faintest five span
14.5$<$$T$$<$15.0.  The fastest five have periods spanning
3.6\,hr$<$$P$$<$6.2\,hr, and the slowest five span
27\,hr$<$$P$$<$38\,hr.
Regarding likely astrometric or visual binaries,
\ngoodhighruwe/\ngoods\ high-quality CQVs have a Gaia DR3 RUWE$>$2;
\nmaybehighruwe/\nmaybes\ of the ambiguous sample share this
characteristic.

@@

The most massive CQVs in our sample might represent an interesting new
regime.  To date, the only stars reported to show the CQV phenomenon
are M-dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2022AJ....163..144G}.  TIC~405754448 and TIC~405910546 however
appear to have masses of $\approx$0.82 and $\approx$0.60\,$M_\odot$
respectively.  The next-highest masses are $\approx$0.40\,$M_\odot$.
The masses for the former two objects are consistent with their CAMD
locations, and their membership in LCC.  Based on its light curve
morphology, TIC~405910546 should be studied in greater depth, to
confirm it is not an eclipsing binary.  TIC~405754448 similarly shows
distinct morphology from many of the CQVs in Figure~\ref{fig:cqvs}, in
that it has some of the lowest amplitude dips.  While TIC~405754448
might be an unresolved binary (RUWE$_{\rm DR3}$=4.7),  the lack of
secondary peaks in its periodogram and the coherent dips present in
the Sector~11 light curve suggest that the CQV signal is indeed from
the apparent primary of the system.  Taken in sum, both of these
objects seem to suggest that the CQV phenomenon extends up in mass to
pre-main-sequence K-dwarfs.
